---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggshadow

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/ggshadow)](https://CRAN.R-project.org/package=ggshadow)
[![License: GPL v2](https://img.shields.io/badge/License-GPL_v2-blue.svg)](https://www.gnu.org/licenses/old-licenses/gpl-2.0.en.html)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

The goal of ggshadow is to provide shadow and glow geoms for points and lines plots created with 'ggplot2'.

## :arrow_double_down: Installation

You can install the development version of ggshadow from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
pak::pkg_install("marcmenem/ggshadow")
```

## :book: Vignette

```{r vignette}
## after installing the package
# vignette("ggshadow", package = "ggshadow")
```

## :chart: Example

### With ggshadow

```{r example}
library(ggplot2)
library(ggshadow)

ggplot(economics_long, aes(date, value01, colour = variable)) +
  geom_shadowline()
```

### Without ggshadow

```{r lineex}
ggplot(economics_long, aes(date, value01, colour = variable)) +
  geom_line()
```

### `ggshadow` supports varying the line color

```{r colorvarex}
ggplot(
  economics_long,
  aes(date, value01,
    group = variable,
    colour = value01,
    shadowsize = 5 * (1 - value01)
  )
) +
  geom_shadowline(
      shadowcolor = "grey",
    shadowalpha = 0.5
  )
```

### `ggshadow` also provides a Neon glow style

```{r example-glow}
ggplot(economics_long, aes(date, value01, color = variable)) +
  geom_glowline() +
  guides(color = "none") +
  theme(
    plot.background = element_rect(fill = "#190132"),
    panel.background = element_rect(fill = "#190132")
  )
```

### Neon glow points

```{r example-glowpoint}
ggplot(mtcars, aes(wt, mpg)) +
  geom_glowpoint(color = "yellow") +
  guides(color = "none") +
  theme(
    plot.background = element_rect(fill = "#190132"),
    panel.background = element_rect(fill = "#190132")
  )
```


### Adding a fill below the neon glow line

```{r example-glowlinefill}
ggplot(
  economics_long[economics_long$variable %in% c("pop", "unemploy"), ],
  aes(date, value01 - 0.5, color = variable, fill = variable)
) +
  geom_glowline() +
  guides(color = "none", shadowcolour = "none", fill = "none") +
  theme(
    plot.background = element_rect(fill = "#190132"),
    panel.background = element_rect(fill = "#190132")
  )
```

